Tail Indices and Scale Parameters in Financial Time Series

### 2017-03-03 papers/FX/draft.tex
First success of generalization.

\subsection{power-law utility function}
In this section we follow Routledge and Zin
\cite{routledge2010generalized} and assume 
that the utility function of consumption $C$ is a power function%
\begin{equation}
  \label{eq:power_utility}
  u(C)=\frac{1}{1-\gamma}C^{1-\gamma}%  
\end{equation}
where $\gamma > 0$. For simplicity we assume the investor
initially has one unit of wealth. Let $r > 0$ be the return on the
risk free state bond and $X$ be the return on equity. Portfolio weights
are $\left(1-\phi\right)$ and $\phi$ respectively. Then
\begin{equation}
  \label{eq:xxie1}
  %% u(C)=\frac{1}{1-\gamma}V^{1-\gamma} \max \left\{
  %% 0, 1 + (1-\phi) r  +\phi X
  %% \right\}^{1-\gamma} \label{3}%
  C = (1 - \phi) e^r + \phi e^X
\end{equation}

%% \subsubsection[in case gamma > 1]{in case $\gamma > 1$}

\subsubsection[in case gamma > 1]{in case $\gamma > 1$}
In this section we consider power utility functions of
\eqref{eq:power_utility} with $\gamma > 1$. For convenience,
let $\xi = \gamma - 1$. In this case, we assume the following
distribution function $F(\cdot)$ of the equity return:
\begin{equation}
  \label{eq:X_distr}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x \leq 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and $K > 0$.
Equation
\eqref{eq:xxie0} can be re-arranged as
\begin{eqnarray}
u(v) &=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) \P[C < \delta v] \nonumber \\
&=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q) \label{eq:functional}
\end{eqnarray}
where
\begin{eqnarray*}
  q(r, \phi) &:=& \ln \left( {
    \delta v - (1 - \phi) e^r
    \over
    \phi
} \right) = \ln\left(
e^r + {\delta v - e^r \over \phi}
\right)
\end{eqnarray*}
Note $C < \delta v$ implies
\[
X < q(r, \phi)
\]
Naturally, if an agent invests in a risky asset instead of a riskless
bond, he expects to obtain a higher return from the risky asset than
he is guarranteed from the riskless bond. In our notation,
this means $\delta v > e^r$, which implies $q(r, \phi) > 0$.
The right-hand-side of \eqref{eq:functional} is a functional of the
distribution function of $X$ via \eqref{eq:xxie1}. For convenience
we denote it $\mathcal U(\cdot)$, i.e.
\[
\mathcal U F (\alpha, \beta, K, K', \phi)
= 
\E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q(r, \phi))
\]
Hereafter we abbreviate $q(r, \phi)$ to just $q$. We have
\begin{eqnarray}
  && \mathcal U F (\alpha, \beta, K, K', \phi) \nonumber \\
  &=&
  -{\alpha K^\alpha \over \xi} p
  \int_{-\infty}^0
      {
       1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
      }
  {1 + b \over (K - x)^{\alpha + 1}} dx
  \nonumber \\
  && -{\beta K'^\beta \over \xi} (1 - p)
  \int_{0}^\infty
  {
   1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
  }
  {1 + b \1{x < q} \over (K' + x)^{\beta + 1}} dx \nonumber \\
  &&
  - b u(\delta v) \left[
    1 - (1 - p) {
      K'^\beta
      \over
      (K' + q)^\beta
    }
  \right]
  \label{eq:xxie1.0}
\end{eqnarray}
Let
\[
G(\alpha, \beta, K, K') =
\max_{0 < \phi \leq 1} \mathcal U F(\alpha, \beta, K, K', \phi)
\]

\begin{theorem} \label{thrm:I}
  Let the disappointment threshold $C < \delta v$ be equivalent to $X
  < q$. Assume $q > 0$. Then $G(\alpha, \beta, K, K')$ is
  monotonically increasing with $\alpha$.
\end{theorem}

\begin{proof}
  We show
  \[
  \td{G}{\alpha} > 0
  \]
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \argmax_{0 < \phi \leq 1}
    \mathcal U F(\alpha, \beta, K, K', \phi)
  \end{equation}
  We have
  \[
  G(\alpha, \beta, K, K') = \mathcal U F(\alpha, \beta, K, K', \hat \phi)
  \]
  It follows
  \begin{eqnarray}
    \td{G}{\alpha}
    &=&
    \pd{\mathcal U F}{\alpha}(\alpha, \beta, K, K', \hat \phi)
    + \pd{\mathcal U F}{\phi}(\alpha, \beta, K, K', \hat \phi)
    \pd{\hat \phi}{\alpha}(\alpha, \beta, K, K')
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies $\forall \alpha > 1$
  \begin{equation}
    \label{eq:xxie4}
    \pd{\mathcal U F}{\phi}(\alpha, \beta, K, K', \hat \phi) = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    \pd{\mathcal U(F)}{\alpha}(\alpha, \beta, K, K', \hat \phi)
    &>& 0
  \end{eqnarray*}
  We have
    \begin{eqnarray*}
      && \pd{\mathcal U(F)}{\alpha}(\alpha, \beta, K, K', \hat \phi) \\
      &=&
      - \frac{\partial}{\partial \alpha} \left\{
        {\alpha p K^\alpha \over \xi} (1 + b)
        \int_{-\infty}^{0}
          \left[
            (1 - \hat\phi) e^r + \hat\phi e^x
          \right]^{-\xi}
          (K - x)^{-\alpha - 1}
        dx \right\} \\
      &=&
      {p \over \xi}
      (1 + b)
      \int_{0}^{\infty}
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-x}
      \right]^{-\xi}
      \left[
        \alpha \ln \left(
          1 + {x \over K}
        \right) - 1
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &=&
      - {p \over \xi}
      (1 + b)
      \int_{0}^{h}
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-x}
      \right]^{-\xi}
      \left[
        1 - \alpha \ln \left(
          1 + {x \over K}
        \right)
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &&
      + {p \over \xi}
      (1 + b)
      \int_{h}^{\infty}
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-x}
      \right]^{-\xi}
      \left[
        \alpha \ln \left(
          1 + {x \over K}
        \right) - 1
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &>&
      - {p \over \xi}
      (1 + b)
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-h}
      \right]^{-\xi}
      \int_{0}^{h}
      \left[
        1 - \alpha \ln \left(
          1 + {x \over K}
        \right)
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &&
      + {p \over \xi}
      (1 + b)
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-h}
      \right]^{-\xi}
      \int_{h}^{\infty}
      \left[
        \alpha \ln \left(
          1 + {x \over K}
        \right) - 1
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &=&
      {p \over \xi}
      (1 + b)
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-h}
      \right]^{-\xi}
      \int_{0}^{\infty}
      \left[
        \alpha \ln \left(
          1 + {x \over K}
        \right) - 1
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &=& 0
    \end{eqnarray*}
    where
    \[
    h = (e^{1/\alpha} - 1)K
    \]
  \end{proof}
Since $u(v)$ given in \eqref{eq:xxie1.0} as a
functional of the distribution function of $X$ is increasing with the
lower tail index $\alpha$, all agents guided by this class of utility
functions will seek the largest $\alpha$ found in a stock group e.g.
a sector. As a result, one can expect all the actively traded equities
in the group to feature the same $\alpha$. In section
\ref{sec:data_analysis} we analyse real-world data of stock returns to
verify this conclusion.

In comparison to the theoretical constancy of $\alpha$, the scale and
shift parameter $K$ in the lower-tail distribution of $X$ may vary
hugely from one equity to another. This could be explained by
\[
\lim_{K \to 0} \td{G}{K}(\alpha, \beta, K, K', \phi) = 0
\]
When $K$ is very small, as is the case in real-world stock return
distributions, a change of $K$ makes little difference to the utility
functional, so its value can vary drastically.

\begin{theorem}
  Assume $K \leq 1$.
  \[
  \lim_{K \to 0} \td{G}{K}(\alpha, \beta, K, K') = 0
  \]
\end{theorem}
\begin{proof}
  By the same argument as in the proof of theorem \ref{thrm:I}, it
  suffices to show
  \begin{eqnarray*}
    \lim_{K \to 0}
    \pd{\mathcal U(F)}{K}(\alpha, \beta, K, K', \hat \phi) &=& 0
  \end{eqnarray*}
  The left-hand-side is
  \begin{eqnarray*}
    && \pd{\mathcal U(F)}{K}(\alpha, \beta, K, K', \hat \phi) \\
    &=&
    -{\alpha p (1 + b) \over \xi}
    \int_{-\infty}^0
    {
      1 \over
      \left[
        (1 - \phi) e^r + \phi e^x
      \right]^\xi
    }
    {
      K^{\alpha - 1}
      (\alpha x + K)
      \over
      (K - x)^{\alpha + 2}
    } dx  \\
    &=&
    {\alpha p (1 + b) \over \xi}
    \int_0^{\infty}
    {
      1 \over
      \left[
        (1 - \phi) e^r + \phi e^x
      \right]^\xi
    }
    {
      K^{\alpha - 1}
      (\alpha x - K)
      \over
      (K + x)^{\alpha + 2}
    } dx
  \end{eqnarray*}
  By reverse Fatou's lemma, it follows
  \begin{eqnarray*}
    &&
    \lim_{K \to 0} \sup_{0 \leq M \leq K}
    \pd{\mathcal U(F)}{K}(\alpha, \beta, K, K', \hat \phi) \\
    &\leq&
    {\alpha p (1 + b) \over \xi}
    \int_0^{\infty}
    {
      1 \over
      \left[
        (1 - \phi) e^r + \phi e^x
      \right]^\xi
    }
    \lim_{K \to 0} \sup_{0 \leq M \leq K}
    {
      M^{\alpha - 1}
      (\alpha x - M)
      \over
      (M + x)^{\alpha + 2}
    } dx
  \end{eqnarray*}
\end{proof}
\section{Review of multivariate GARCH models:
  same tail index or not}
Many multivariate GARCH models imply a common tail index for all
series under consideration, e.g. the Orthogonal GARCH model of
Alexander and Chibumba (1997) \cite{alexander1997multivariate}, its
generalization GO-GARCH of van der Weide (2002) \cite{van2002go}, as
well as the Full Factor GARCH model of Vrontos et al (2003)
\cite{vrontos2003full} and the Generalized Orthogonal Factor GARCH
model of Lanne and Saikkonen (2007) \cite{lanne2007modeling}. These
models are characterized by their treatment of each series as a linear
combination of factors, and each of the factors is modeled as a GARCH
process. As a result of this treatment, each and every series under
consideration necessarily has the lowest of the tail indices of its
contributing factors (cf. Mikosch (2013) \cite{Mikosch2013} as well
as Andersen, Davis, Kreiss and Mikosch (2009)
\cite{andersen2009handbook}).

@@

\section{Hill Estimator}
%% TODO: Show Hill estimates of real and simulated data with confidence
%% band. Argue that all estimated tail indices are indistinguishable
%% given the confidence band.
There have been several estimators for the tail index proposed in the
literature, e.g. Hill (1975) \cite{hill1975simple}, Pikands (1975)
\cite{pickands1975statistical}, Dekkers and Einmahl and De Haan (1989)
\cite{dekkers1989moment}. See also Embrechts and Kl\"uppelberg and
Mikosch (1997)\cite{Embrechts1997}. The most popular of these is
arguably Hill (1975) \cite{hill1975simple}:
\[
\hat \alpha = \left[
  {1 \over k} \sum_{i=1}^k \ln {x_{(i)} \over x_{(k+1)}}
  \right]^{-1}
\]
where $x_{(i)}$ is the $i$-th upper order statistic of a sample
$x_1, x_2, ..., x_n$. It has been shown that the Hill estimator is
applicable to 
\begin{itemize}
\item iid random variables (Mason (1982) \cite{mason1982laws})
\item a weakly dependent sequence (Rootz{\'e}n, Leadbetter,
  and de Haan \cite{rootzen1992tail})
\item a linear process (Resnick and St{\u{a}}ric{\u{a}} (1995)
  \cite{resnick1995consistency}).
\end{itemize}
In these cases it is shown that, if $k \to \infty$ and $k/n \to 0$
as $n \to \infty$, the Hill estimator is weakly consistent, i.e.
\[
\sqrt k (\hat \alpha - \alpha) \overset{d}{\to} N(0, \alpha^2)
\]

\subsubsection{The Energy and the Consumer Staples sectors of S\&P 500}
Figure \ref{fig:Energy_Hill_upper},
\ref{fig:Consumer_Staples_Hill_upper},
and \ref{fig:Information_Technology_lower}
show the Hill estimates of the
lower tail indices of the ``energy'', ``consumer staples'' and ``information
technology'' sectors of the S\&P 500 index, respectively.
\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Energy_Hill_upper.pdf}
  \caption{Hill estimates of the upper tail indices of 32 stocks'
    daily return series in the {\it Energy} sector of Standard \& Poor
    500 index. Each circle coresponds to a Hill estimate; the grey
    triangles above and below it mark the 97.5\% and 2.5\% quantiles
    of its approximate normal distribution.
    The low and high red lines mark the median of the 2.5\% quantiles
    and median of the 97.5\% quantiles, respectively.
    The data are from {\it Yahoo Finance} and the labels on
    the horizontal axis are Yahoo symbols of the stocks. The data span
    from 2010-01-01 to 2015-01-01 and comprise $n=1304$
    observations. $k=(\ln n)^2 = 49$ upper order statistics are used
    for computing $\alpha_n$. 
  }
  \label{fig:Energy_Hill_upper}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Consumer_Staples_Hill_upper.pdf}
  \caption{Hill estimates of the upper tail indices of 30 stocks'
    daily return series in the {\it Consumer Staples} sector of
    Standard \& Poor 500 index.
  }
  \label{fig:Consumer_Staples_Hill_upper}
\end{figure}

@@

\section{Hybrid estimation of the assumed distribution function}
We adopt a hybrid procedure to estimate the parameters of the
distribution function assumed in eq.\eqref{eq:X_distr}: First we
obtain a Hill estimate of the lower- and upper-tail indices of an
equity return and fix $\alpha$ and $\beta$ in \eqref{eq:X_distr}
to their Hill estimates. Then we estimate $K$ and $K'$ by maximizing
the likelihood function with fixed $\alpha$ and $\beta$.

@@

%% What is the probability of rejecting the null hypothesis when the test
%% is applied to $(X_1, X_2)$ where $X_1$ and $X_2$ have tail indices
%% $\kappa_1 \neq \kappa_2$? The probability of wrongly rejecting the
%% null hypothesis must be lower than $\alpha$.
\textcolor{red}{Review the test of Hoga}

\section{Data Analysis} \label{sec:data_analysis}
\subsection{Tail index and scale parameter}
In this section we apply the statistical tools reviewed in the
previous sections to real stock return series, denoted $X_t$
hereafter. We are interested in finding out the tail indices and the
scale parameters of the stationary distribution of $|X_t|$.

@@

Using Pickands' estimator, the same result of very similar tail indices
is again obtained for the {\it Energy} and the {\it Consumer Staples}
sectors. Figure \ref{fig:Energy_Pickands} and
\ref{fig:Consumer_Staples_Pickands} illustrate this claim.
\begin{figure}[htb!]
  \includegraphics[width=\textwidth]{Energy_Pickands.pdf}
  \caption{Pickands' estimates of {\it Energy} stocks.}
  \label{fig:Energy_Pickands}
\end{figure}

>>>>

Routledge and Zin \cite{routledge2010generalized} assumed
a power-law utility function of $C$:
\begin{equation}
  \label{eq:power_utility}
  u(C)=\frac{1}{1-\gamma}C^{1-\gamma}%  
\end{equation}
where $\gamma > 0$. For our discussion it suffices that $u(\cdot)$ is
an increasing function. For simplicity we assume the investor
initially has one unit of wealth. Let $r > 0$ be the return on the
risk free state bond and $X$ be the return on equity. Portfolio weights
are $\left(1-\phi\right)$ and $\phi$ respectively. Then
\begin{equation}
  \label{eq:xxie1}
  %% u(C)=\frac{1}{1-\gamma}V^{1-\gamma} \max \left\{
  %% 0, 1 + (1-\phi) r  +\phi X
  %% \right\}^{1-\gamma} \label{3}%
  C = (1 - \phi) e^r + \phi e^X
\end{equation}
For the distribution of $X$, call it $F(\cdot)$, we assume
%% \subsubsection[in case gamma > 1]{in case $\gamma > 1$}
% \subsection{power-law utility function}
% \subsubsection[in case gamma > 1]{in case $\gamma > 1$}
% In this section we consider power utility functions of
% \eqref{eq:power_utility} with $\gamma > 1$. For convenience,
% let $\xi = \gamma - 1$. In this case, we assume the following
% distribution function $F(\cdot)$ of the equity return:
\begin{equation}
  \label{eq:X_distr}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x \leq 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and $K > 0$.
Equation \eqref{eq:xxie0} can be re-arranged as
\begin{eqnarray}
u(v) &=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) \P[C < \delta v] \nonumber \\
&=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q) \label{eq:functional}
\end{eqnarray}
where
\begin{eqnarray*}
  q(r, \phi) &:=& \ln \left( {
    \delta v - (1 - \phi) e^r
    \over
    \phi
} \right) = \ln\left(
e^r + {\delta v - e^r \over \phi}
\right)
\end{eqnarray*}
Note $C < \delta v$ implies
\[
X < q(r, \phi)
\]
Naturally, if an agent invests in a risky asset instead of a riskless
bond, he expects to obtain a higher return from the risky asset than
he is guarranteed from the riskless bond. In our notation,
this means $\delta v > e^r$, which implies $q(r, \phi) > 0$.
The right-hand-side of \eqref{eq:functional} is a functional of the
distribution function of $X$ via \eqref{eq:xxie1}. For convenience
we denote it $\mathcal U(\cdot)$, i.e.
\[
\mathcal U F (\alpha, \beta, K, K', \phi)
= 
\E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q(r, \phi))
\]
Hereafter we abbreviate $q(r, \phi)$ to just $q$. We have
\begin{eqnarray}
  && \mathcal U F (\alpha, \beta, K, K', \phi) \nonumber \\
  &=&
  \alpha K^\alpha  p
  \int_{-\infty}^0
  u\left[ (1 - \phi) e^r + \phi e^x \right]
  {1 + b \over (K - x)^{\alpha + 1}} dx
  \nonumber \\
  &&
  \beta K'^\beta (1 - p)
  \int_{0}^\infty
  u\left[ (1 - \phi) e^r + \phi e^x \right]
  {1 + b \1{x < q} \over (K' + x)^{\beta + 1}} dx \nonumber \\
  &&
  - b u(\delta v) \left[
    1 - (1 - p) {
      K'^\beta
      \over
      (K' + q)^\beta
    }
  \right]
  \label{eq:xxie1.0}
\end{eqnarray}
Let
\[
G(\alpha, \beta, K, K') =
\max_{0 < \phi \leq 1} \mathcal U F(\alpha, \beta, K, K', \phi)
\]

\begin{theorem} \label{thrm:I}
  Let the disappointment threshold $C < \delta v$ be equivalent to $X
  < q$. Assume $q > 0$. Also assume $u(\cdot)$ is an increasing function.
  Then
  \[
  \td{G}{K} < 0 < \td{G}{\alpha}
  \]
\end{theorem}

\begin{proof}
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \argmax_{0 < \phi \leq 1}
    \mathcal U F(\alpha, \beta, K, K', \phi)
  \end{equation}
  We have
  \[
  G(\alpha, \beta, K, K') = \mathcal U F(\alpha, \beta, K, K', \hat \phi)
  \]
  It follows
  \begin{eqnarray}
    \td{G}{\alpha}
    &=&
    \pd{\mathcal U F}{\alpha}(\alpha, \beta, K, K', \hat \phi)
    + \pd{\mathcal U F}{\phi}(\alpha, \beta, K, K', \hat \phi)
    \pd{\hat \phi}{\alpha}(\alpha, \beta, K, K')
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies $\forall \alpha > 1$
  \begin{equation}
    \label{eq:xxie4}
    \pd{\mathcal U F}{\phi}(\alpha, \beta, K, K', \hat \phi) = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    \pd{\mathcal U(F)}{\alpha}(\alpha, \beta, K, K', \hat \phi)
    &>& 0
  \end{eqnarray*}
  We have
    \begin{eqnarray*}
      && \pd{\mathcal U(F)}{\alpha}(\alpha, \beta, K, K', \hat \phi) \\
      &=&
      - \frac{\partial}{\partial \alpha} \left\{
        {\alpha p K^\alpha \over \xi} (1 + b)
        \int_{-\infty}^{0}
          \left[
            (1 - \hat\phi) e^r + \hat\phi e^x
          \right]^{-\xi}
          (K - x)^{-\alpha - 1}
        dx \right\} \\
      &=&
      {p \over \xi}
      (1 + b)
      \int_{0}^{\infty}
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-x}
      \right]^{-\xi}
      \left[
        \alpha \ln \left(
          1 + {x \over K}
        \right) - 1
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &=&
      - {p \over \xi}
      (1 + b)
      \int_{0}^{h}
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-x}
      \right]^{-\xi}
      \left[
        1 - \alpha \ln \left(
          1 + {x \over K}
        \right)
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &&
      + {p \over \xi}
      (1 + b)
      \int_{h}^{\infty}
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-x}
      \right]^{-\xi}
      \left[
        \alpha \ln \left(
          1 + {x \over K}
        \right) - 1
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &>&
      - {p \over \xi}
      (1 + b)
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-h}
      \right]^{-\xi}
      \int_{0}^{h}
      \left[
        1 - \alpha \ln \left(
          1 + {x \over K}
        \right)
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &&
      + {p \over \xi}
      (1 + b)
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-h}
      \right]^{-\xi}
      \int_{h}^{\infty}
      \left[
        \alpha \ln \left(
          1 + {x \over K}
        \right) - 1
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &=&
      {p \over \xi}
      (1 + b)
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-h}
      \right]^{-\xi}
      \int_{0}^{\infty}
      \left[
        \alpha \ln \left(
          1 + {x \over K}
        \right) - 1
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &=& 0
    \end{eqnarray*}
    where
    \[
    h = (e^{1/\alpha} - 1)K
    \]
    As for $\td{G(\alpha, \beta, K, K')}{K}$, by the same argument as for
    $\td{G(\alpha, \beta, K, K')}{\alpha}$, it suffices to show
    \[
    \pd{\mathcal U(F)}{K}(\alpha, \beta, K, K', \hat\phi) < 0
    \]
    We have
    \begin{eqnarray*}
      && \pd{\mathcal UF}{K}(\alpha, \beta, K, K', \hat\phi) \\
      &=&
      -{\alpha p (1+ b) \over \xi}
      \int_0^\infty
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-x}
      \right]^{-\xi}
      {
        K^{\alpha - 1} (\alpha x - K)
        \over
        (K + x)^{\alpha + 2}
      }
      dx \\
      &=&
      -{\alpha p (1+ b) \over \xi}
      \left\{
        - \int_{0}^{K/\alpha}
        \left[
          (1 - \hat\phi) e^r + \hat\phi e^{-x}
        \right]^{-\xi}
        {
          K^{\alpha - 1} (K - \alpha x)
          \over
          (K + x)^{\alpha + 2}
        }
        dx \right. \\
      &&
      \left.
        +
        \int_{K/\alpha}^{\infty}
        \left[
          (1 - \hat\phi) e^r + \hat\phi e^{-x}
        \right]^{-\xi}
        {
          K^{\alpha - 1} (\alpha x - K)
          \over
          (K + x)^{\alpha + 2}
        }
        dx
      \right\} \\
      &<&
      -{\alpha p (1+ b) \over \xi}      
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-M/\alpha}
      \right]^{-\xi} \times \\
      &&
      \left\{
        \int_{K/\alpha}^{\infty}
        {
          K^{\alpha - 1} (\alpha x - K)
          \over
          (K + x)^{\alpha + 2}
        }
        dx
        - \int_{0}^{K/\alpha}
        {
          K^{\alpha - 1} (K - \alpha x)
          \over
          (K + x)^{\alpha + 2}
        }
        dx
      \right\} \\
      &=& 0
    \end{eqnarray*}
  \end{proof}
Since $u(v)$ given in \eqref{eq:xxie1.0} as a
functional of the distribution function of $X$ is increasing with the
lower tail index $\alpha$ and decreasing with $K$, there is a curve of
equal preference on the plane of $(\alpha, K)$. Moving along this
curve in the direction of increasing $\alpha$, one expects the values
of $K$ to increase too, i.e. the estimated values of $\alpha$ and $K$
should appear positively correlated. This is indeed the case in some
real stock return data, e.g. the ``Energy'' and ``Information Technology''
sectors of S\&P 500 companies. This is illustrated in figures
\ref{fig:Energy_alpha_K} and \ref{fig:Information_Technology_alpha_K}.

% all agents guided by this class of utility
% functions will seek the largest $\alpha$ and the smallest $K$ found in
% a stock group e.g. a sector.

% As a result, one can expect all the
% actively traded equities in the group to feature the same $\alpha$ and
% $K$. However, the estimated value of $K^\alpha$ may vary
% significantly. This can be understood as a result of the smallness of
% $K$, which as revealed in section \ref{sec:hybrid_estimation} is of the
% order of $10^{-2}$, and the inaccuracy of the estimated value of
% $\alpha$, which typically ranges from 2.5 to 5. Exponentiation hugely
% magnifies the inaccuracy in $\alpha$.

\section{Review of multivariate GARCH models:
  same tail index or not}
Many multivariate GARCH models imply a common tail index for all
series under consideration, e.g. the Orthogonal GARCH model of
Alexander and Chibumba (1997) \cite{alexander1997multivariate}, its
generalization GO-GARCH of van der Weide (2002) \cite{van2002go}, as
well as the Full Factor GARCH model of Vrontos et al (2003)
\cite{vrontos2003full} and the Generalized Orthogonal Factor GARCH
model of Lanne and Saikkonen (2007) \cite{lanne2007modeling}. These
models are characterized by their treatment of each series as a linear
combination of factors, and each of the factors is modeled as a GARCH
process. As a result of this treatment, each and every series under
consideration necessarily has the lowest of the tail indices of its
contributing factors (cf. Mikosch (2013) \cite{Mikosch2013} as well
as Andersen, Davis, Kreiss and Mikosch (2009)
\cite{andersen2009handbook}).

@@

\section{Hill Estimator}
There have been several estimators for the tail index proposed in the
literature, e.g. Hill (1975) \cite{hill1975simple}, Pikands (1975)
\cite{pickands1975statistical}, Dekkers and Einmahl and De Haan (1989)
\cite{dekkers1989moment}. See also Embrechts and Kl\"uppelberg and
Mikosch (1997)\cite{Embrechts1997}. The most popular of these is
arguably Hill (1975) \cite{hill1975simple}:
\[
\hat \alpha = \left[
  {1 \over k} \sum_{i=1}^k \ln {x_{(i)} \over x_{(k+1)}}
  \right]^{-1}
\]
where $x_{(i)}$ is the $i$-th upper order statistic of a sample
$x_1, x_2, ..., x_n$. It has been shown that the Hill estimator is
applicable to 
\begin{itemize}
\item iid random variables (Mason (1982) \cite{mason1982laws})
\item a weakly dependent sequence (Rootz{\'e}n, Leadbetter,
  and de Haan \cite{rootzen1992tail})
\item a linear process (Resnick and St{\u{a}}ric{\u{a}} (1995)
  \cite{resnick1995consistency}).
\end{itemize}
In these cases it is shown that, if $k \to \infty$ and $k/n \to 0$
as $n \to \infty$, the Hill estimator is weakly consistent, i.e.
\[
\sqrt k (\hat \alpha - \alpha) \overset{d}{\to} N(0, \alpha^2)
\]

%% \subsubsection{The Energy and the Consumer Staples sectors of S\&P 500}
Figure \ref{fig:Energy_lower},
\ref{fig:Consumer_Staples_lower},
and \ref{fig:Information_Technology_lower}
show the Hill estimates of the
lower tail indices of the ``energy'', ``consumer staples'' and ``information
technology'' sectors of the S\&P 500 index, respectively.
\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Energy_lower.pdf}
  \caption{Hill estimates of the lower tail indices of 32 stocks'
    daily return series in the {\it Energy} sector of Standard \& Poor
    500 index. Each circle coresponds to a Hill estimate; the grey
    triangles above and below it mark the 97.5\% and 2.5\% quantiles
    of its approximate normal distribution.
    The low and high red lines mark the median of the 2.5\% quantiles
    and median of the 97.5\% quantiles, respectively.
    The data are from {\it Yahoo Finance} and the labels on
    the horizontal axis are Yahoo symbols of the stocks. The data span
    from 2010-01-01 to 2015-01-01 and comprise $n=1304$
    observations. $k=(\ln n)^2 = 49$ lower order statistics are used
    for computing $\alpha_n$. 
  }
  \label{fig:Energy_lower}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Consumer_Staples_lower.pdf}
  \caption{Hill estimates of the lower tail indices of 30 stocks'
    daily return series in the {\it Consumer Staples} sector of
    Standard \& Poor 500 index.
  }
  \label{fig:Consumer_Staples_lower}
\end{figure}

@@

\section{Hybrid estimation of the assumed distribution function}
\label{sec:hybrid_estimation}
We adopt a hybrid procedure to estimate the parameters of the
distribution function assumed in \eqref{eq:X_distr}: First we
obtain a Hill estimate of the lower-tail indices of an
equity return and fix $\alpha$ in \eqref{eq:X_distr}
to its Hill estimate. Then we estimate $K$ by maximizing
the likelihood function with fixed $\alpha$. Obviously we take only
negative observations and hence condition on $X < 0$.

Figure \ref{fig:Energy_alpha_K},
\ref{fig:Consumer_Staples_alpha_K},
and \ref{fig:Information_Technology_alpha_K}
show the estimates of $K$ alongside the Hill estimates of $\alpha$ of
the ``energy'', ``consumer staples'' and ``information
technology'' sectors of the S\&P 500 index, respectively.

\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Energy_alpha_K.pdf}
  \caption{Hybrid estimates of the lower-tail parameters of daily
    return series in the {\it Energy} sector of S\&P
    500 index.
  }
  \label{fig:Energy_alpha_K}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Consumer_Staples_alpha_K.pdf}
  \caption{Hybrid estimates of the lower-tail parameters of daily
    return series in the {\it Consumer Staples} sector of S\&P
    500 index.
  }
  \label{fig:Consumer_Staples_alpha_K}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Information_Technology_alpha_K.pdf}
  \caption{Hybrid estimates of the lower-tail parameters of daily
    return series in the {\it Information Technology} sector of S\&P
    500 index.
  }
  \label{fig:Information_Technology_alpha_K}
\end{figure}

@@

%% What is the probability of rejecting the null hypothesis when the test
%% is applied to $(X_1, X_2)$ where $X_1$ and $X_2$ have tail indices
%% $\kappa_1 \neq \kappa_2$? The probability of wrongly rejecting the
%% null hypothesis must be lower than $\alpha$.
%% \textcolor{red}{Review the test of Hoga}

% \section{Data Analysis} \label{sec:data_analysis}
% \subsection{Tail index and scale parameter}
% In this section we apply the statistical tools reviewed in the
% previous sections to real stock return series, denoted $X_t$
% hereafter. We are interested in finding out the tail indices and the
% scale parameters of the stationary distribution of $|X_t|$.

@@
